% Dr. Pintao - Curriculum Vitae
% Copyright 2020 Pintao Lyu
% Email: pintao.lyu@outlook.com
% Web: https://geoffboeing.com/
% Repo: https://github.com/gboeing/cv

\documentclass[12pt,letterpaper]{report}
\usepackage{lmodern}
\usepackage[T1]{fontenc} % output T1 font encoding (8-bit) so accented characters are a single glyph
\usepackage[utf8]{inputenc} % allow input of utf-8 encoded characters
\usepackage[strict,autostyle]{csquotes} % smart and nestable quote marks
\usepackage[USenglish]{babel} % automatically regionalize hyphens, quote marks, etc
\usepackage{microtype} % improves text appearance with kerning, etc
\usepackage{datetime} % enable formatting of date output
\usepackage{tabto} % make nice tabbing
\usepackage{hyperref} % enable hyperlinks and pdf metadata
\usepackage{geometry} % manually set page margins
\usepackage{enumitem} % enumerate with [resume] option
\usepackage{titlesec} % allow custom section fonts
\usepackage{marvosym} % For cool symbols.
\usepackage{hyperref}
\usepackage[a5paper, landscape]{geometry} % demo only
\usepackage{hyperref}

\usepackage{paracol}
\usepackage{multicol}

% what is your name?
\newcommand{\myname}{Pintao Lyu}

% define a default font face and set it as the body font
\usepackage{crimson} % document's serif font
\usepackage{helvet}  % document's sans serif font

% define how far to tab for list items with left-aligned date - different font faces need different widths
\newcommand{\listtabwidth}{1.75cm}

% set name font to title the document
\newcommand{\namefont}[1]{{\normalfont\bfseries\Huge{#1}}}

% set section heading fonts and before/after spacing
\SetTracking{encoding=*}{20}
\titleformat{\section}{\sffamily\small\bfseries\lsstyle\uppercase}{}{}{}{}
\titlespacing{\section}{0pt}{24pt plus 4pt minus 2pt}{12pt plus 2pt minus 2pt}

% set subsection heading fonts and before/after spacing
\titleformat{\subsection}{\sffamily\footnotesize\bfseries}{}{}{}{}
\titlespacing{\subsection}{0pt}{12pt plus 4pt minus 2pt}{8pt plus 2pt minus 2pt}

% set page margins
\geometry{body={6.5in, 9.0in},
    left=1.0in,
    top=1.0in}

% prevent paragraph indentation
\setlength\parindent{0em}

% define space between list items
\newcommand{\listitemspace}{0.15em}

% make unordered lists without bullets and use compact spacing
\renewenvironment{itemize}
{\begin{list}{}{\setlength{\leftmargin}{0em}
            \setlength{\parskip}{0em}
            \setlength{\itemsep}{\listitemspace}
            \setlength{\parsep}{\listitemspace}}}
    {\end{list}}

% make tabbed lists so content is left-aligned next to years
\TabPositions{\listtabwidth}
\newlist{tablist}{description}{3}
\setlist[tablist]{leftmargin=\listtabwidth,
    labelindent=0em,
    topsep=0em,
    partopsep=0em,
    itemsep=\listitemspace,
    parsep=\listitemspace,
    font=\normalfont}

% print the month and year only when using \today
\newdateformat{monthyeardate}{\monthname[\THEMONTH] \THEYEAR}

% define hyperlink appearance and metadata for pdf properties
\hypersetup{
    colorlinks  = true,
    urlcolor    = black,
    pdfauthor   = {\myname},
    pdfkeywords = {Risk management, Actuarial science, Household finance},
    pdftitle    = {\myname: Curriculum Vitae},
    pdfsubject  = {Curriculum Vitae},
    pdfpagemode = UseNone
}

\begin{document}
    \raggedright

    % display name as the document title
    \namefont{\myname}

    % contact info
    \vspace{1em}
    \begin{minipage}[t]{0.68\textwidth}
        Department of Econometrics and Operations Research \\
        Tilburg School of Economics and Management \\
        Tilburg University
%        Tilburg,North Brabant, NL
    \end{minipage}
    \begin{minipage}[t]{0.31\textwidth}
        Email: \href{mailto:pintao.lyu@outlook.com}{pintao.lyu@outlook.com} \\
        Phone: +31 06 83 39 26 89 \\
        %Web: \href{https://geoffboeing.com/}{https://geoffboeing.com/}
    \end{minipage}
    \vspace{0.5em}



    \section*{Education}

    \begin{tablist}

        \item[Ph.D.] \tab Econometrics and Operations Research, Tilburg University, 2017-2020 (expected) \\
        Visiting scholar at The University of Melbourne (Host: Prof. Johnny Siu-Hang Li)
        \item[M.Phil.]  \tab Economics \textit{with distinction}, Tilburg University, 2015-2017 \\
        Key courses: The economics and finance of the pension (9.5/10.0), Life cycle investment and pension systems (9.0/10.0), Asset liability management (8.5/10.0), Valuation and risk management (8.5/10.0)

        \item[B.Sc.]  \tab Economics \textit{with honor}, Central University of Finance and Economics, 2011-2015

    \end{tablist}






    \section*{Research Areas}

    \begin{itemize}

        \item Household finance, Risk management, Actuarial science

    \end{itemize}

    \section*{Teaching Experience}

\subsection*{Tilburg University}

\begin{itemize}
	
	\item Econometrics (B.Sc. Econometrics and Operations Research), 2018
	\item Evaluations: 4.42/5.00 (peer average: 4.00/5.00)
	
\end{itemize}




    \section*{Papers}

	\subsection*{Job market paper}

	\begin{tablist}
	
	\item[2019-] \tab  Lyu, P., \enquote{Heterogeneous survival expectations and wealth inequality}

	\medskip
	
	\textit{Abstract:}\\
	
	Using new survey evidence in Heimer et al. (2019, Journal of Finance), I show how subjective life expectancy leads to wealth inequality. Agents with higher educational attainment switch from underestimating to overestimating survival earlier in life, which results in higher saving motives when young and slower asset drawdown when old. Educational attainment positively correlates with living conditions, causing various degrees of agents' overreaction to salient risks in the vicinity. I characterize a standard stochastic life cycle model to these subjective mortality beliefs and demonstrate that heterogeneous survival expectations contribute to retirement wealth inequality. 
	
	% prediction
	% results
	
	\medskip
	
	\textit{Key skills:}\\
	Used Stata to process survey and estimate reduced-form econometrics models. Used MATLAB and Fortran to simulate the life cycle model and match the model outputs to the data moments. Used the parallel computing environment in the Lisa Cluster to streamline the simulations.

	
	\end{tablist}

    \subsection*{Articles in Peer-Reviewed Journals}

    \begin{tablist}
    	\item[2020] \tab Lyu, P., De Waegenaere, A., \& Melenberg, B. (2020) \enquote{A multi-population approach to forecasting all-cause mortality using cause-of-death mortality data.} \textit{North American Actuarial Journal}, 1-36. %\href{https://doi.org/10.1177/0308518X19869678}{doi:10.1177/0308518X19869678}\\
    	\medskip
    	
    	\textit{Key skills:}\\
		Used SQL to process a large-scale WHO database. Used R to visualize the data. Used MATLAB to construct statistical tests and forecast time series.



    \end{tablist}



    \subsection*{Working papers}

    \begin{tablist}
        
        \item[2018-] \tab Lyu, P., De Waegenaere, A., \& Melenberg, B. \enquote{A quantitative comparison of simulation strategies for longevity risk management.} 
        
        \medskip
        
        \textit{Key skills:}\\
		Assessed the asymptotic validity of various bootstrap schemes using a simulation study in MATLAB.
        
        \item[2019-] \tab Lyu, P., Zhou, K. Q., \& Li, J. S. H. \enquote{Incorporating the association between socioeconomic status and mortality into index-based longevity hedges.}
        
        \medskip
        
        \textit{Key skills:}\\
       	Evaluated the hedge effectiveness of the newly proposed index-based hedges in Python.
        


    \end{tablist}

 \section*{Professional Experience}

\begin{tablist}
	
	\item[2016--] \tab Nationale-Nederlanden Life, Quantitative Researcher, 2 days a week\\
	\medskip
	\textit{Involved projects:}\\
	Longevity Redesign: wrote a technical model document of an internal model for approx. €2 bn longevity trend risk and implemented it in R jointly with Anastasios Bardoutsos, supervised by Wilbert Ouburg.\\
	
	\medskip
	
	Mortality Differentiation: extended a mortality model to price pension contracts differently for various salary thresholds in MATLAB jointly with Ahmad Salahnejhad, supervised by David Schrager.
	
	\medskip
	
	

	
\end{tablist}


    \section*{Conference and seminars}


    \begin{tablist}
		\item[2019] \tab Fifteenth International Longevity Risk and Capital Markets Solutions Conference (Longevity 15).
		
        \item[2018] \tab 22nd International Congress on Insurance: Mathematics and Economics, Fourteenth International Longevity Risk and Capital Markets Solutions Conference, European Actuarial Journal Conference 2018, Netspar International Pension Workshop ’18, The Asia-Pacific Risk and Insurance Association Conference 2018, Invited seminar at The University of Melbourne.
        
        \item[2017] \tab Thirteenth International Longevity Risk and Capital Markets Solutions Conference (Longevity 13).
  

    \end{tablist}



    \section*{Grants and Awards}

    \subsection*{Awards and Honors}

    \begin{tablist}

        \item[2018] \tab Kyobo Life Travel Scholarship 



    \end{tablist}

    \subsection*{Grants}
    % and Fellowships

    \begin{tablist}

   
        \item[2019] \tab Longer life, longer in good health, working longer? Implications of educational differences for the pension system, Netspar Thema grant. Project member. 
        
        \item[2018] \tab  Modeling and forecasting Chinese population dynamics in a multi-population context (\$10,000). Society of Actuaries China research grant. Co-PI with Hong Li and Yang Lu.
        
        \item[2017] \tab An investigation into Differentiated longevity trends within the Dutch population. Netspar Ph.D. grant with Nationale-Nederlanden Life and Tilburg University. Supervisor: Bertrand Melenberg and David Schrager.


    \end{tablist}




    	\section*{Programming Skills}
    	
    	%    \subsection*{Software}
    	
    	\begin{itemize}
    		
    		\item MATLAB, R, Stata, SQL, Python
    		
    	\end{itemize}
    	

%	\section*{Reference}
%\begin{itemize}
%	\item Bertrand Melenberg, Professor of Econometrics and Finance,  B.Melenberg@tilburguniversity.edu
%	\item Anja De Waegenaere, Professor of Actuarial Science and Accounting, A.M.B.DeWaegenaere@tilburguniversity.edu
%\end{itemize}
\section*{Teaching Reference}

	
Dr. Pavel Cizek\\
Tilburg University\\	
\href{mailto:p.cizek@uvt.nl}{p.cizek\textrm{@}uvt.nl}

	

\section*{Research Reference}
\begin{multicols}{3}
	
	Prof. Bertrand Melenberg\\
	Tilburg University\\
	 \href{mailto:B.Melenberg@uvt.nl}{b.melenberg\textrm{@}uvt.nl}
	 
	 \vfill\columnbreak
	 
	 Prof. Anja De Waegenaere\\
	 Tilburg University\\ \href{mailto:a.m.b.dewaegenaere@uvt.nl}{a.m.b.dewaegenaere\textrm{@}uvt.nl}
	
	\vfill\columnbreak

	Prof. Johnny Siu-Hang Li\\
	The University of Melbourne\\ \href{mailto:johnny.li@unimelb.edu.au}{johnny.li\textrm{@}unimelb.edu.au}
	
\end{multicols}




    \begin{center}
        %\vspace{6em}
        \vfill
        Updated \monthyeardate\today
    \end{center}





\end{document}
